Toward theories of deliberated preferences

### 2020-12-07 simple.tex
Falsifiability of a claim in general (too general, interruptus)

>>>>

It is now necessary to verify that, first, the claim of convincingness is falsifiable, and second, that it suffices to prove validity.

Let us first clarify what falsifiability formally means in our context. Define a claim $C \subseteq \powerset{I × \allhist × \Phi}$ as a subset of the possible relations $\leadsto$. When a theory claims that $C$, it claims that $\leadsto$ is indeed a member of $C$. Say that a set of observations $O \subseteq I × \allhist × \Phi$ falsifies the claim $C$ iff $C \cap \set{R \subseteq O} = \emptyset$. In such a case, $C$ contains no possible relation $R$ compatible with the observations in $O$, or in other words, the observations $O$ prove that ${\leadsto} \notin C$. Say that $C$ is falsifiable iff some finite set of observation falsifies it.
\begin{example}[Two claims]
	Given a normative theory and $\phi \in \Phi$, the claim $C_1 = \set{{\leadsto} \subseteq I × \allhist × \Phi \suchthat \forall i \in I, \exists \ar \in \allargs \suchthat \ar \ileadstost \phi}$ corresponds to claiming that for all individuals $i \in I$, some argument is $i$-decisive for $\phi$. If the set of arguments is infinite, $C_1$ is not falsifiable.  
	Given $\ar \in \allargs$ and $\phi \in \Phi$, the set $C_2 = \set{{\leadsto} \subseteq I × \allhist × \Phi \suchthat \forall i \in I, \ar \ileadstost \phi}$ denotes the claim that all individuals will consider the argument $\ar$ as decisive for $\phi$. This claim is falsified by any observation such that $\hist \nileadsto \phi$ for some $\hist \in \allhist$ with $\ar \in \histend$, thus, $C_2$ is falsifiable.
\end{example}

Let the claim of a descriptive theory by defined as $C = …$.
\begin{theorem}
	…
